---
title: "IMDB Box Office Analysis"
author: "Anand Narasimhan"
date: "7/1/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
options(scipen=999)
```

## The data

The source data for this was downloaded from Kaggle at <https://www.kaggle.com/deepmatrix/imdb-5000-movie-dataset/downloads/movie_metadata.csv.zip>.

We'll be looking at `gross` as the outcome. We'll do some pre-processing to remove any `NA` values from the data set as well as convert string factors into numeric values so that we can better create a model.

```{r message=FALSE}

imdb <- read.csv("data/movie_metadata.csv")
imdb<- imdb[complete.cases(imdb),]
imdb <- as.data.frame(lapply(imdb,as.numeric))
names(imdb)[9:15]
```

## Elminating predictors

We'll eliminate zero variance and correlated predictors with the `nearZeroVar` and `cor` functions

```{r messages=FALSE,warning=FALSE}
nearZeroVar(imdb,names = TRUE)
descrCor <-  cor(imdb)
findCorrelation(descrCor,names = TRUE)
imdb <- imdb[,-nearZeroVar(imdb)]
imdb <- imdb[,-findCorrelation(descrCor)]
```

## Identifying variable importance

```{r echo=TRUE}
inTrain <- createDataPartition(y=imdb$gross,p=0.75, list=FALSE)
training <- imdb[inTrain,]
testing <- imdb[-inTrain,]
modFit <- lm(gross~.,data=training)
imp <- varImp(modFit)
imp$predictor <- row.names(imp)
imp[imp$Overall>=10,]
```

Based on the table above, we'll use `num_voted_users` as the only predictor for our model

## Testing our model prediction

```{r echo=FALSE}
modFit <- lm(gross~num_voted_users,data=training)
pred <- predict(modFit,testing)
df <- data.frame(prediction=pred,actual=testing$gross)
df$diff <- df$prediction-df$actual
plot(df$diff)
```

Predicted box office gross for `50,000` votes would be $`r prettyNum(round(predict(modFit,newdata = data.frame(num_voted_users=50000)),0),big.mark=",")`
